%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\ProcessOptions\relax

\documentclass[letterpaper,11pt]{article}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{newtxtext,newtxmath}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{tabu}
\usepackage[parfill]{parskip}
\usepackage[left=0.75in,top=0.5in,right=0.75in,bottom=0.5in]{geometry}

% For spcaed small caps
\usepackage{microtype}


\setlist{noitemsep, topsep=-1\parskip}
\renewcommand{\labelitemi}{$\bullet$}



%--------------------------------------------------------------------------------
%                                   Constants                                   -
%--------------------------------------------------------------------------------


  \def\namespaceskip{0.575em}
  \def\afterheaderspace{1.1pt}
 

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \spaceskip \namespaceskip \relax
  \textbf{\Huge{Zahid Safi}} \\ \vspace{1pt}
    \small 801-635-0123 $|$ \href{mailto:zahidsafi956@gmail.com}{{zahidsafi956@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/zahidsafi}{{https://www.linkedin.com/in/zahidsafi}} $|$
    \href{https://github.com/ZahidSafi}{{https://github.com/ZahidSafi}} 
\end{center}

%-----------EXPERIENCE-----------

\section{\textbf{Experience}}
\begin{itemize}[leftmargin=0.05in, label={}]
	\item{
	            \begin{tabu} {X[l] X[c] X[r]}
		            \textbf{Backend Software Developer} & \textbf{BambooHR} & \textbf{May 2021 -- Mar 2023} \\
	            \end{tabu}
	            \begin{itemize}[label=$\bullet$]
		            \item{Operated with scrum teams implementing business logic and specifications from product management
					and UX
					to deliver functional culture/insights solutions, to contribute to HR processes for over 20,000 customers.}
		            \item{Collaborated on an employee well-being survey feature with UX team, creating a data collection
					system that analyzed over 500+ responses, provided crucial insights for executive decision-making.}
		            \item {Employed CI/CD (Continuous Integration and Continuous Development) technology to deliver
					features to production daily and ensuring code quality by following proper software development design.}
		            \item{Developed a training widget meeting business requirement to provide updates on completed,
					incomplete, and overdue training increasing completion rates for companies having 100+ trainings.}
		            \item{Optimized SQL queries to enhance data base performance for organizations with over 1,000 employees,
					reducing loading times by 40\% and improving user experience.}
	            \end{itemize}
	      }

	\item{
	            \begin{tabu} {X[l] X[c] X[r]}
		            \textbf{IAM Intern} & \textbf{University of Utah} & \textbf{Feb 2020 -- Apr 2021} \\
	            \end{tabu}

	            \begin{itemize}[label=$\bullet$]
		            \item{Tailored a Spring Boot app for streamlined user attribute management utilizing Apereo CAS, Git, and
					Linux.}
		            \item{Built a JSON file management using Java, Git and Linux to update, create and manage JSON
					files for CAS.}
	            \end{itemize}
	      }

	\item{
	            \begin{tabu} {X[l] X[c] X[r]}
		            \textbf{Microsoft Support} & \textbf{Education At Work} & \textbf{Jan 2018 -- Feb 2020} \\
	            \end{tabu}
	            \begin{itemize} [label=$\bullet$]
		            \item{Troubleshot and resolved Office Suite technical issues for 100+ clients in a timely and professional
					manner,
					boosting customer satisfaction ratings by 20\%.}
		            \item{Outperformed competing support sites by delivering efficient and effective solutions, enhancing
					customer retention and loyalty to the organization.}
		            \item{Collaborated with colleagues using articles, reducing response time and enhancing first-contact
					resolution, helping 2x as many customers and doubling productivity.}
	            \end{itemize}
	      }

\end{itemize}

%-----------TECHNICAL SKILLS-----------

\section{\textbf{Skills}}
\begin{itemize}[leftmargin=0.05in, label={}]
	{\item{
		            \textbf{Languages}{: PHP, C\#, Java, C, C++, Python, MySQL, SQL, JavaScript, HTML, CSS} \\
		            \textbf{Frameworks And Libraries}{: .NET Core, ASP.NET Core, React.js, FastAPI} \\
		            \textbf{Developer Tools}{: Git, GitHub , Azure, Postman, AWS(EC2), Docker, Linux, Jira, CI/CD} \\
					\textbf{Soft Skills}{: Communication, Teamwork \& Collaboration, Problem-Solving, Adaptability, Debugging/Troubleshooting} \\
		      }}
\end{itemize}


%-----------PROJECTS-----------

\section{\textbf{Projects}}
\begin{itemize}[leftmargin=0.05in, label={}]
	\item{
	            \textbf{Personal Portfolio Website}
	            \begin{itemize} [label=$\bullet$]
		            \item{Coded a React app to showcase overall work experience, projects, and skills.}
		            \item {Deployed on Netlify using CI/CD to automate the deployment process and making the app publicly
					accessible.}
	            \end{itemize}
	      }
	\item{
	            \textbf{Sorting Algorithm Visualizer}
	            \begin{itemize} [label=$\bullet$]
		            \item{Developed a React app to visualize algorithm efficiency to help understand algorithmic concepts and performance.}
	            \end{itemize}
	      }
	\item{
	            \textbf{U-Dash: Remote Campus Delivery Vehicle}
	            \begin{itemize} [label=$\bullet$]
		            \item{Devised a campus vehicle using Raspberry Pi, Python, and C to provide efficient remote deliveries.}
		            \item {Implemented a REST API with FastAPI to establish communication between the vehicle and web
					application.}
		            \item{Built and deployed a ReactJS web application, enabling communication between the user
					and vehicle.}

	            \end{itemize}
	      }
	\item{
	            \textbf{Research Opportunity Web Platform}
	            \begin{itemize} [label=$\bullet$]
		            \item{Created an MVC web app using HTML5, CSS3, C\#, and MySQL to connect students with research opportunities.}
		            \item{Implemented a RESTful API
					with ASP.NET Core, enabling data transfer between the app and MySQL database.}
	            \end{itemize}
	      }
	\item{
	            \textbf{FFMPEG: Innovative Audio Codec}
	            \begin{itemize} [label=$\bullet$]
		            \item{Engineered an ASIF codec in C for FFMPEG, streamlining encoding/decoding of audio data in ASIF
					format.}
	            \end{itemize}
	      }

\end{itemize}



%-----------EDUCATION-----------

\section{\textbf{Education}}
\begin{itemize}[leftmargin=0.05in, label={}]
	\item{
	            \begin{tabu} {X[l] X[c] X[r]}
		            \textbf{Salt Lake City, Utah} & \textbf{University of Utah} & \textbf{Aug 2017 -- Dec 2022} \\
	            \end{tabu}

	            \begin{itemize} [label=$\bullet$]
		            \item{Bachelor of Science in Computer Engineering - 3.7 GPA}
		            \item{Relevant Courses{: Object-Oriented Programming, Data Structures \& Algorithm, Web Software Architecture, Computer Systems, Software Practice 1 \& 2, Database Systems, Computer Network} }
	            \end{itemize}
	      }
\end{itemize}


%-------------------------------------------
\end{document}
