%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,1pt]{article}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\input{glyphtounicode}






% Adjust margins
\addtolength{\oddsidemargin}{-.75in}
\addtolength{\evensidemargin}{-.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
  \textbf{\Huge Zahid Safi} \\ \vspace{1pt}
  \small 801-635-0123 $|$ \href{mailto:zahidsafi956@gmail.com}{{zahidsafi956@gmail.com}} $|$
  \href{https://www.linkedin.com/in/zahidsafi}{{https://www.linkedin.com/in/zahidsafi}} $|$
  \href{https://github.com/ZahidSafi}{{https://github.com/ZahidSafi}} $|$
  \href{https://zahid-safi.netlify.app/}{https://zahid-safi.netlify.app/}
\end{center}


%-----------EXPERIENCE-----------

\section{\textbf{Experience}}
\begin{itemize}[leftmargin=0.15in, itemsep=0pt, parsep=0pt, label={}]
  \item{
              \textbf{Software Developer, Backend} \hfill May 2021 -- March 2023 \\
              BambooHR \hfill Lindon, Utah \\
              \begin{itemize}
                \item{Collaborated with team using PHP and MySQL to deliver culture solutions and insights for BambooHR customers by creating a fully functional solutions.}
                \item{Co-led the development of an intuitive survey feature that streamlined data collection and analysis for executives resulting in an increase in employee well-being tracking efficiency and improvement in response rates.}
                \item{Pioneered a dynamic training widget to provide real-time updates on completed, pending, and overdue training tasks to increase training completion rates.}
                \item{Faced with slow database performance for organizations with over 1,000 employees, optimized MySQL queries to reduce loading times by 40\% and improve UX.}
              \end{itemize}
        }

  \item{
              \textbf{Identity and Access Management Intern} \hfill May 2021 -- March 2023 \\
              University of Utah \hfill Salt Lake City, Utah \\
              \begin{itemize}
                \item{Partnered to modernize the University’s login page using Apereo CAS, Git, Tomcat, HTML, and Linux.}
                \item{Tailored a Spring Boot app for streamlined user attribute management utilizing Apereo CAS, Git, and Linux.}
                \item{ Efficiently administered CAS JSON files leveraging Java, Git, and Linux for seamless updates and organization.}
              \end{itemize}
        }

  \item{
              \textbf{Microsoft Support} \hfill May 2021 -- March 2023 \\
              Education At Work \hfill Salt Lake City, Utah \\
              \begin{itemize}
                \item{Boosted customer satisfaction and five-star ratings by effectively resolving Office Suite technical issues.}
                \item{Outperformed competing support sites with exceptional service, increasing customer retention and positive
                            feedback.}
                \item{Improved customer support with colleagues using OneNote and articles, reducing response time and enhancing
                            first-contact resolution.}
              \end{itemize}
        }

\end{itemize}

%-----------TECHNICAL SKILLS-----------

\section{\textbf{Technical Skills}}
\begin{itemize}[leftmargin=0.15in, itemsep=0pt, parsep=0pt, label={}]
  \small{\item{
                \textbf{Languages}{: PHP, C\#, Java, C, C++, Python, MySQL,  JavaScript, HTML, CSS} \\
                \textbf{Frameworks/Libraries}{: .NET Core, ASP.NET Core, React.js, FastAPI} \\
                \textbf{Developer Tools}{: GitHub , Azure, Postman, AWS} \\
          }}
\end{itemize}


%-----------PROJECTS-----------

\section{\textbf{Projects}}
\begin{itemize}[leftmargin=0.15in, itemsep=0pt, parsep=0pt, label={}]
  \item{
              \textbf{Sorting Algorithm Visualizer} \hfill May 2021 -- March 2023 \\
              \begin{itemize}
                \item{Developed a HTML/CSS/JS and React app to visualize algorithm efficiency, boosting user understanding}
              \end{itemize}
        }
  \item{
              \textbf{U-Dash: Remote Campus Delivery Vehicle} \hfill May 2021 -- March 2023 \\
              \begin{itemize}
                \item{Conceptualized and built a campus vehicle using Raspberry Pi, Python, and C for remote deliveries.}
                \item{Devised and deployed a user-centric web application with FastAPI and React for an enhanced UX.}
                \item{Implemented a REST API with FastAPI and Python to facilitate communication between the vehicle and web app.}
              \end{itemize}
        }
  \item{
              \textbf{Research Opportunity Web Platform} \hfill May 2021 -- March 2023 \\
              \begin{itemize}
                \item{Crafted an MVC ASP.NET Core web app using HTML/CSS, C\#, and SQL to connect students with research opportunities.}
                \item{Designed a user-friendly interface with HTML/CSS and Bootstrap to enhance the user experience.}
                \item{Implemented a REST API with ASP.NET Core and C\# to facilitate communication between the web app and database.}
              \end{itemize}
        }
  \item{
              \textbf{FFMPEG: Innovative Audio Codec} \hfill May 2021 -- March 2023 \\
              \begin{itemize}
                \item{Engineered an ASIF codec in C for FFMPEG, streamlining encoding/decoding of audio data in ASIF format.}
              \end{itemize}
        }

\end{itemize}



%-----------EDUCATION-----------

\section{\textbf{Education}}
\begin{itemize}[leftmargin=0.15in, itemsep=0pt, parsep=0pt, label={}]
  \item{
              \textbf{University of Utah - 3.7 GPA} \hfill Salt Lake City, Utah \\
              Bachelor of Science in Computer Engineering \hfill Dec 2022 \\
              Deans List, Fall 2017 - Spring 2020
              \begin{itemize}[leftmargin=0.01in, label={}]
                \small{\item{
                              \textbf{Relevant Courses}{: Object-Oriented Programming, Data Structures \& Algorithm, Web Software Architecture, Computer Systems, Software Practice I \& II, Database Systems, Computer Network, Embedded Systems} \\
                        }}

              \end{itemize}
        }
\end{itemize}


%-------------------------------------------
\end{document}
